---
title: "Negroni Week Venue Map"
author: "Winston Saunders"
date: "June 3, 2015"
output: pdf_document
---

__This map__ of the Portland area bars participating in [Negroni Week](negroniweek.com) is provided without warranty. Heck, it's an experiment. 

_Use at your own peril._

###Note on methods:  
1.  Venues were downloaded directly from the Negoni Week website.  
2.  GPS coordinates were derived from online sources including Bing and Open Maps.  
3.  Charity Type is categorized by me.  

###Intended Usages:  
This list is for entertainment only. However, if one were to plan a crawl with a specific Charity Type in mind, this list might aid in theoretical planning. 

```{r, echo=FALSE}
Directory <- "/Users/winstonsaunders/Documents/Negroni_week/"
file<-"Negroni_week_PDX.csv"

venues<-read.csv(paste0(Directory, file))

    ## center map
    mid_lon=(min(venues$longitude)+max(venues$longitude))/2
    mid_lat=(min(venues$latitude)+max(venues$latitude))/2



```

#Number of venues by Charity Type.  

```{r echo=FALSE, message=FALSE, results="asis", warning=FALSE}
require(xtable)
venues_cats<-as.data.frame(t(table(venues$Type)))[,c(2,3)]
colnames(venues_cats)<-c("Charity Type", "Number")
print(xtable(venues_cats), floating=FALSE)
```

#Number of venues by Zip Code  

Only zip codes with three or more venues listed  

```{r echo=FALSE, message=FALSE, results="asis"}
require(xtable)
venues_cats<-as.data.frame(t(table(venues$Postal...Zip.Code)))[,c(2,3)]
colnames(venues_cats)<-c("Charity Type", "Number")

print(xtable(venues_cats[venues_cats$Number>2,]), floating=FALSE)
```

#Greater Portland Area Map  


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, results='asis'}
require(ggmap)
require(mapproj)

##Subset data by crime
## here focus on only top crimes
        ##get map data
        map <- get_map(source="google", maptype="roadmap", location = c(lon = mid_lon, lat = mid_lat), zoom = 12)
        ##generate map
        map1 <- ggmap(map) 

        ## 
        map1<-map1 + geom_point(aes(x = longitude, y = latitude, color=factor(Type)), data = venues, alpha = .8, size = 4) 
        map1<-map1+theme(legend.title=element_blank())
        map1<-map1+ggtitle("Negroni Week Venues and Charity Type")
        print(map1)
```

#Downtown Map

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
require(ggmap)
require(mapproj)

##Subset data by crime
## here focus on only top crimes
        ##get map data
        map <- get_map(source="google", maptype="roadmap", location = "Portland", zoom = 14)
        ##generate map
        map1 <- ggmap(map) 

        ## 
        map1<-map1 + geom_point(aes(x = longitude, y = latitude, color=factor(Type)), data = venues, alpha = .8, size = 4) 
        map1<-map1+theme(legend.title=element_blank())
        map1<-map1+ggtitle("Negroni Week Venues and Charity Type")
        print(map1)
```
  
    
      
        
          
            
#Venue List   



```{r, echo=FALSE, results="asis", message=FALSE}

require(xtable)

venues_table=as.data.frame(venues[,c(1,3)])

print(xtable(venues_table), floating=FALSE)  
```