---
title: "Negroni Week Venue Map"
author: "Winston Saunders"
date: "June 3, 2015"
output: pdf_document
---

This map of the Portland area Negoni Week participating bars generated from the list published on the official [Negroni Week website](negroniweek.com).  Particpants are coded by the Charity Type.

_Charity Type is my interpretation and I take no responsibility for its accuracy or for inaccuracies. Use is at your own peril._

Note on methods:  
1.  Venues were downloaded directly from the Negoni Week Website.  
2.  GPS coordinates of addresses were derived from online sources including Bing and Open Maps.  
3.  Charity Type is categorized by me.  

Intended Usages:  
This list is for entertainment only. However, if one were to plan a crawl with a specific Charity Type in mind, this list might aid in deciding a trajoctory and minimizing Uber fares. 

```{r, echo=FALSE}
Directory <- "/Users/winstonsaunders/Documents/Negroni_week/"
file<-"Negroni_week_PDX.csv"

venues<-read.csv(paste0(Directory, file))

    ## center map
    mid_lon=(min(venues$longitude)+max(venues$longitude))/2
    mid_lat=(min(venues$latitude)+max(venues$latitude))/2


```

#Greater Portland   

```{r, echo=FALSE, message=FALSE, warning=FALSE}
require(ggmap)
require(mapproj)

##Subset data by crime
## here focus on only top crimes
        ##get map data
        map <- get_map(source="google", maptype="roadmap", location = c(lon = mid_lon, lat = mid_lat), zoom = 12)
        ##generate map
        map1 <- ggmap(map) 

        ## 
        map1<-map1 + geom_point(aes(x = longitude, y = latitude, color=factor(Type)), data = venues, alpha = .8, size = 4) 
        map1<-map1+theme(legend.title=element_blank())
        map1<-map1+ggtitle("Negroni Week Venues and Charity Type")
        print(map1)
```

#Downtown

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
require(ggmap)
require(mapproj)

##Subset data by crime
## here focus on only top crimes
        ##get map data
        map <- get_map(source="google", maptype="roadmap", location = "Portland", zoom = 14)
        ##generate map
        map1 <- ggmap(map) 

        ## 
        map1<-map1 + geom_point(aes(x = longitude, y = latitude, color=factor(Type)), data = venues, alpha = .8, size = 4) 
        map1<-map1+theme(legend.title=element_blank())
        map1<-map1+ggtitle("Negroni Week Venues and Charity Type")
        print(map1)
```

#Venues   



```{r, echo=FALSE, results="asis", message=FALSE}

require(xtable)

venues_table=as.data.frame(venues[,c(1,3)])

print(xtable(venues_table))  
```